Is high social class always beneficial for survival? Long-term perspectives of social inequality in mortality among adults and elderly in Northern Sweden 1851--2013

### 2017-07-29 article.Rmd
Small corection in title

---
title: "Is high social class always beneficial for survival? Long-term perspectives of social inequality in mortality among adults and elderly in Northern Sweden 1851--2013""
author: Sören Edvinsson and Göran Broström
date: "24 July 2017"
output:
  bookdown::pdf_document2:
    number_sections: yes
    toc: yes
    toc_depth: 2
  bookdown::html_document2:
    number_sections: yes
    toc: yes
    toc_depth: 2
    toc_float: yes
link-citations: yes
bibliography: mybib.bib
biblio-style: apalike
---

>>>>

---
title: "Is high social class always beneficial for survival? Long-term perspectives of social inequality in mortality among adults and elderly in Northern Sweden 1851--2013"
author: Sören Edvinsson and Göran Broström
date: "24 July 2017"
output:
  bookdown::pdf_document2:
    number_sections: yes
    toc: yes
    toc_depth: 2
  bookdown::html_document2:
    number_sections: yes
    toc: yes
    toc_depth: 2
    toc_float: yes
link-citations: yes
bibliography: mybib.bib
biblio-style: apalike
---
